% Compile with pdflatex visitor_report.tex

\documentclass[a4paper,oneside,12pt,pdftex]{article}

\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{times}
%%\usepackage{hyperref}
\usepackage{varioref}
\usepackage{amsmath}
\usepackage{amssymb}

\renewcommand{\O}{\mathrm{O}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\m}{\mbox}

\everymath{\displaystyle}
\setlength{\headheight}{0cm}
\setlength{\headsep}{0cm}
\setlength{\topmargin}{0cm}
\setlength{\oddsidemargin}{0cm} \setlength{\evensidemargin}{0cm}
\setlength{\textheight}{24cm}
\setlength{\textwidth}{16.2cm}

\usepackage{url}

\title{Visitor Research Report}

\date{}

\begin{document}

\maketitle

\textbf{
\begin{tabular}{ll}
Visitor Name:&Pierre Roux\\
&\\
Area of Research:&Formal Methods\\
\\
Period of Visit:&February 26 - April 16, 2009
\end{tabular}
}

\vspace{2cm}

\noindent\textbf{Aim:}
\vspace{0.1cm}

\noindent Investigate the use of edge valued decision diagrams for representing general 
arithmetic expressions. Comparing saturation algorithm against currently used model-checking 
libraries.

\vspace{0.8cm}
\noindent\textbf{Strategy:}
\vspace{0.1cm}

\noindent Compare theoretically edge valued diagrams against currently used arithmetic diagrams. 
Implement a little model checker using both saturation and current libraries.

\vspace{0.8cm}
\noindent\textbf{Accomplishments:}
\vspace{0.1cm}

\noindent Edge valued diagrams have been theoretically proved not worse than arithmetic 
diagrams. Experimental results with our implementation show the interest of edge valued diagrams 
and saturation.

\vspace{0.8cm}
\noindent\textbf{Future Work:}
\vspace{0.1cm}

\noindent Document and release library. Using it in SAL model checker.

\vspace{0.8cm}
\noindent\textbf{Pending Publications:}
\vspace{0.1cm}

\noindent NIA Technical Report

\vspace{0.8cm}
\noindent\textbf{Seminar Presented:}
\vspace{0.1cm}

\noindent "Model checking with edge-valued decision diagrams"\\
April 15 , NIA Room 141

\clearpage

\noindent\textbf{Note: Brief report addressing all areas mentioned abovenot to exceed 3 pages.}
\vspace{0.8cm}

\noindent Binary decision diagrams (BDD) are the cornerstone of symbolic model checking. The 
efficient encoding and manipulation of boolean functions with BDDs have facilitated significant 
advances in automated system verification. Traditionally, BDDs are also used for encoding 
arithmetic functions, but the efficiency of this encoding is not equally efficient.

\vspace{0.8cm}

\noindent Variations and extensions of BDDs have been proposed for more specific, purposes, 
without a major impact, especially when dealing with arithmetic functions.

\vspace{0.8cm}

\noindent We propose the use of edge-valued decision diagrams (EVMDD) for a more efficient 
encoding of general arithmetic expressions. We show that distributing values along the paths in 
the diagram dramatically increases the chances of sharing subdiagrams, hence providing a more 
compact representation.

\vspace{0.8cm}

\noindent We have implemented a complete algebra of EVMDDs in an ANSI C library as a back-end 
for symbolic model checking. We compare its performance to CUDD, the most widely used decision 
diagram library. For specific types of arithmetic expressions, such as some polynomials (which 
are the foundation of the hybrid abstraction technique being developed in support of NASA's IVHM 
project), EVMDDs are clearly superior to ADDs.

\end{document}
